---
title: "EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('..'))
```


```{r}
load.project
```
#TO FIND ANY UNKNOW VALUES
```{r}
x=cyber.security.4_leaving.survey.responses
unique(x)
```
```{r}
summary(x)
```
#Understanding each of the table separtely for betterment of cleaning the data
```{r}
unique(x$id)
```
```{r}
unique(x$learner_id)
```
```{r}
unique(x$left_at)
```
```{r}
unique(x$leaving_reason)
```
```{r}
unique(x$last_completed_step_at)
```
```{r}
unique(x$last_completed_step)
```
```{r}
unique(x$last_completed_week_number)
```
```{r}
unique(x$last_completed_step_number)
```
#Different types/techinques of cleaning the data
1. Remove Irrelevant Values
2. Get Rid of Duplicate Values
3. Avoid Typos (and similar errors)
4. Convert Data Types
5. Take Care of Missing Values
#Creating a dataframe without any missing values.
```{r}
x1=na.omit(x)
unique(x1)
summary(x1)
```
```{r}
gender_plot = ggplot(x1, aes(y = factor(leaving_reason))) + 
  geom_bar(stat = "count", width = 0.7, fill = "steelblue") + theme_minimal() 
gender_plot
```

```{r}
gender_plot = ggplot(x, aes(x = factor(leaving_reason))) + 
  geom_bar(stat = "count", width = 0.7, fill = "steelblue") + theme_minimal() 
gender_plot
```



```{r}
ggplot(x1,aes(x=learner_id, y=id, fill=leaving_reason))+
  geom_bar(stat = "identity",color="darkblue",position = position_dodge())
```


























#--------------------------------------------------------------------------------------

#Analysis of cyber.secrity 4
```{r}
cs4=cyber.security.4_video.stats
summary(cs4)
```
```{r}
dim(cs4)
head(cs4)
```
#Plotting the video stats
```{r}
ggplot(cs4,aes(y=title,x=step_position))+
  geom_bar(stat = "identity",color="green",position = position_dodge())
  
```
#Analysis of title with video_duration
```{r}
ggplot(cs4,aes(y=title,x=video_duration))+
  geom_bar(stat = "identity",color="green",position = position_dodge())
```
#Analysis of total views
```{r}
ggplot(cs4,aes(y=title,x=total_views,))+
  geom_col(stat = "identity",color="green",position = position_dodge())
```

```{r}
pie <- ggplot(cs4, aes(x = "", fill = factor())) + 
  geom_bar(width = 1) +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="class", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of class", 
       caption="Source: mpg")
  
pie + coord_polar(theta = "y", start=0)
```

```{r}
index=cs4[9,15]
index
```

