---
title: "EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('..'))
```


```{r}
load.project
```
#TO FIND ANY UNKNOW VALUES
```{r}
x=cyber.security.4_leaving.survey.responses
unique(x)
```
```{r}
summary(x)
```
#Understanding each of the table separtely for betterment of cleaning the data
```{r}
unique(x$id)
```
```{r}
unique(x$learner_id)
```
```{r}
unique(x$left_at)
```
```{r}
unique(x$leaving_reason)
```
```{r}
unique(x$last_completed_step_at)
```
```{r}
unique(x$last_completed_step)
```
```{r}
unique(x$last_completed_week_number)
```
```{r}
unique(x$last_completed_step_number)
```
#Different types/techinques of cleaning the data
1. Remove Irrelevant Values
2. Get Rid of Duplicate Values
3. Avoid Typos (and similar errors)
4. Convert Data Types
5. Take Care of Missing Values
#Creating a dataframe without any missing values.
```{r}
x1=na.omit(x)
unique(x1)
summary(x1)
```
```{r}
gender_plot = ggplot(x1, aes(y = factor(leaving_reason))) + 
  geom_bar(stat = "count", width = 0.7, fill = "steelblue") + theme_minimal() 
gender_plot
```

```{r}
gender_plot = ggplot(x, aes(x = factor(leaving_reason))) + 
  geom_bar(stat = "count", width = 0.7, fill = "steelblue") + theme_minimal() 
gender_plot
```



```{r}
ggplot(x1,aes(x=learner_id, y=id, fill=leaving_reason))+
  geom_bar(stat = "identity",color="darkblue",position = position_dodge())
```


























#--------------------------------------------------------------------------------------

#Analysis of cyber.secrity 4
```{r}
cs4=cyber.security.4_video.stats
summary(cs4)
```
```{r}
dim(cs4)
head(cs4)
```
#Plotting the video stats
```{r}
ggplot(cs4,aes(y=title,x=step_position))+
  geom_bar(stat = "identity",color="green",position = position_dodge())
  
```
#Analysis of title with video_duration
```{r}
ggplot(cs4,aes(y=title,x=video_duration))+
  geom_bar(stat = "identity",color="green",position = position_dodge())
```
#Analysis of total views
```{r}
ggplot(cs4,aes(y=title,x=total_views,))+
  geom_col(stat = "identity",color="green",position = position_dodge())
```

```{r}
pie <- ggplot(cs4, aes(x = "", fill = factor())) + 
  geom_bar(width = 1) +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="class", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of class", 
       caption="Source: mpg")
  
pie + coord_polar(theta = "y", start=0)
```

#Lollipop plot
```{r}
index=cs4[,c(9:15)]
index
ggplot(cs4, aes(y=title, x=viewed_five_percent)) + 
  geom_point(size=3) + 
  geom_segment(aes(y=title, 
                   yend=title, 
                   x=0, 
                   xend=viewed_five_percent))
```
#--------------------------------------------------------------------------------------


#Task which i am doing is that comparing the various variable from the dataset which is given for cybersecurity. So i am comparing the 1st iteration with the last two itertaion to know whther there is a decrease in ppl taking the course.
#Taking the enrolment dataset which was used of the first iteration. 
```{r}
cs=cyber.security.4_enrolments
```
#Loading the dataset into cs1 for data cleaning.
#Different types/techinques of cleaning the data
1. Remove Irrelevant Values
2. Get Rid of Duplicate Values
3. Avoid Typos (and similar errors)
4. Convert Data Types
5. Take Care of Missing Values
#Data Cleaning on the dataset.
1.There are no irrelevant values in the dataset and all data variables are related.
2.Removing the duplicate values.As we can tell from the output that there are no duplicate values in the dataset.
3.There are no similar errors in the dataset.
4.Convert Data Types. Since all the data available in the dataset is of similar data type, Therefore there is no conversion needed.
5.Omitting the missing values.
At-last, cs4 variable contains the cleaned dataset.
```{r}
a=duplicated(cs)#to check whether there is any duplicate data in the data set.
a
b=sapply(a, class)#to check whether the data given is of same data type.
b
cs4=na.omit(cs)
summary(cs4)
```
#Starting the analysing process.
Viewing the number of students enrolled for the course and also checking gender wise for the 1st iteration.
```{r}
s_enrolled=length(unique(cs4$learner_id))
s_enrolled
s_enrolled_gender=table(cs4$gender)
s_enrolled_gender
gender_plot = ggplot(cs1, aes(x = factor(gender))) + 
  geom_bar(stat = "count", width = 0.7, fill = "Red") + theme_minimal() 
gender_plot
pie =gender_plot + coord_polar("y", start=0)+ scale_fill_brewer(palette="Dark2")
pie #should ask.
```



```{r}
employment_plot = ggplot(cyber.security.3_enrolments, aes(x = factor(employment_status))) + 
  geom_bar(stat = "count", width = 0.7, fill = "orange") + theme_minimal() + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
employment_plot
```



```{r}
en_students=as.data.frame(table(cs4$detected_country))
#removing the row without country code.
enrolled_students=en_students[-c(1),]
table(enrolled_students$country)
#selecting the countries with more than 65 enrollments
countries_with_more_than_65_enrollment=enrolled_students[enrolled_students$Freq>65,]
countries_with_more_than_65_enrollment %>%
ggplot(aes(reorder(Var1,-Freq),Freq))+
  geom_col(stat="identity", fill="green",alpha=.8,width = .6)+
  labs(title="No of Students Enrolled vs Countries",x="Countires",
  y="No. of Students Enrolled")+
  theme(plot.title = element_text(hjust = 0.5)) #how to count
```

#We can check how many students are getting unenrolled from leaving survey response dataset and calculate the percentage of students unenrolled from the course.
For 1st iteration.
```{r}
students_unenrolled1=length(cyber.security.1_leaving.survey.responses$left_at)
students_unenrolled1 #Number of students unenrolled at 1st iteration
s_enrolled1=length(unique(cyber.security.1_enrolments$learner_id))#Number of students enrolled
s_enrolled1
Percentage_unenrolled1=(students_unenrolled1/s_enrolled1)*100
Percentage_unenrolled1
```
For 2nd iteration
```{r}
students_unenrolled2=length(cyber.security.2_leaving.survey.responses$left_at)
students_unenrolled2 #Number of students unenrolled at 1st iteration
s_enrolled2=length(unique(cyber.security.2_enrolments$learner_id))#Number of students enrolled
s_enrolled2
Percentage_unenrolled2=(students_unenrolled2/s_enrolled2)*100
Percentage_unenrolled2
```
For 3rd iteration
```{r}
students_unenrolled3=length(cyber.security.3_leaving.survey.responses$left_at)
students_unenrolled3 #Number of students unenrolled at 1st iteration
s_enrolled3=length(unique(cyber.security.3_enrolments$learner_id))#Number of students enrolled
s_enrolled3
Percentage_unenrolled3=(students_unenrolled3/s_enrolled3)*100
Percentage_unenrolled3
```
For 4th iteration
```{r}
students_unenrolled=length(cyber.security.4_leaving.survey.responses$left_at)
students_unenrolled #Number of students unenrolled
s_enrolled #Number of students enrolled
Percentage_unenrolled=(students_unenrolled/s_enrolled)*100
Percentage_unenrolled
```
For 5th iteration
```{r}
students_unenrolled5=length(cyber.security.5_leaving.survey.responses$left_at)
students_unenrolled5 #Number of students unenrolled at 1st iteration
s_enrolled5=length(unique(cyber.security.5_enrolments$learner_id))#Number of students enrolled
s_enrolled5
Percentage_unenrolled5=(students_unenrolled5/s_enrolled5)*100
Percentage_unenrolled5
```
For 6th iteration
```{r}
students_unenrolled6=length(cyber.security.6_leaving.survey.responses$left_at)
students_unenrolled6 #Number of students unenrolled at 1st iteration
s_enrolled6=length(unique(cyber.security.6_enrolments$learner_id))#Number of students enrolled
s_enrolled6
Percentage_unenrolled6=(students_unenrolled6/s_enrolled6)*100
Percentage_unenrolled6
```
For 7th iteration
```{r}
students_unenrolled7=length(cyber.security.7_leaving.survey.responses$left_at)
students_unenrolled7 #Number of students unenrolled at 1st iteration
s_enrolled7=length(unique(cyber.security.7_enrolments$learner_id))#Number of students enrolled
s_enrolled7
Percentage_unenrolled7=(students_unenrolled7/s_enrolled7)*100
Percentage_unenrolled7
```
From the above calculation we can tell that, for the first 3 iteration, the percentage of unenrolled  is 0.But for the 4th iteration there is an increase from 0 to 2%.Likewise, the percentage for 5th, 6th and 7th is 5%,3%, 3.5% respectively.



#Checking the main reason for leaving the course for 4th iteration.
```{r}
gender_plot = ggplot(cyber.security.4_leaving.survey.responses, aes(y = factor(leaving_reason))) + 
  geom_bar(stat = "count", width = 0.7, fill = "steelblue") + theme_minimal() 
gender_plot
```

```{r}
merge=merge.data.frame(cyber.security.4_leaving.survey.responses,cyber.security.4_enrolments,on="learner_id")
unenrolled_students=as.data.frame(table(merge$detected_country))
countries_with_more_than_3_unenrollment=unenrolled_students[unenrolled_students$Freq>3,]
countries_with_more_than_3_unenrollment %>%
ggplot(aes(reorder(Var1,-Freq),Freq))+
  geom_bar(stat="identity", fill="black",alpha=.8,width = .6)+
    labs(title="No of Students Unenrolled vs Countries",x="Countires",
      y="No. of students unenrolled")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
students_unerolled_plot=as.data.frame(table(cyber.security.4_leaving.survey.responses$leaving_reason))
ggplot(students_unerolled_plot,aes(reorder(Var1,Freq),Freq))+
  geom_bar(stat="identity", fill="#f68060", alpha=.8, width=.5) +
    coord_flip() +
   labs(title="No of students unenrolled vs reasons",x="Reasons",y="No .of students unenrolled")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
ggplot(cyber.security.4_video.stats,aes(y=title,x=total_views,))+
  geom_col(stat = "identity",color="green",position = position_dodge())
```


```{r}
g=ggplot(cyber.security.4_video.stats)
g+geom_path(aes(x=step_position,y=europe_views_percentage,colour='Europe view percentage'))+
geom_path(aes(x=step_position,y=oceania_views_percentage,colour='Oceania view percentage'))+
geom_path(aes(x=step_position,y=asia_views_percentage,colour='Asia view percentage'))+
geom_path(aes(x=step_position,y=north_america_views_percentage,colour='North America view percentage'))+
geom_path(aes(x=step_position,y=south_america_views_percentage,colour='South America view percentage '))+
geom_path(aes(x=step_position,y=africa_views_percentage,colour='Africa view percentage'))+
scale_color_discrete("Pattern")+xlab("step position")+ylab("viewed percentage")
```

```{r}
enrollment.list=list(cyber.security.1_enrolments,cyber.security.2_enrolments,cyber.security.3_enrolments,cyber.security.4_enrolments,cyber.security.5_enrolments,cyber.security.6_enrolments,cyber.security.7_enrolments)

students_enrollements_over_7_runs=lapply(enrollment.list, function(cs4) length(unique(cs4$unenrolled_at)))
students=data.frame(students_enrollements_over_7_runs)
colnames(students)=c("1st time","2nd time ","3rd time","4th time","5th time","6th time","7th time")
students
```

