---
title: "EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('..'))
```
#----------------------------EDA PROJECT----------------------------------------------
The goal of this project is to examine (EDA) the cyber-security course data files acquired from each run by FutureLearn, a company that offers free cyber-security courses both online and offline.
The project follows the CRISP DM methodology.
CRISP DM methodology:The CRISP-DM (CRoss Industry Standard Process for Data Mining) is a six-phase process model that accurately captures the data science life cycle. It functions as a series of guidelines to assist you in planning, organizing, and implementing your data science (or machine learning) project.
1.Business understanding - What does the business need?
2.Data understanding – What data do we have / need? Is it clean?
3.Data preparation – How do we organize the data for modeling?
4.Modeling – What modeling techniques should we apply?
5.Evaluation – Which model best meets the business objectives?
6.Deployment – How do stakeholders access the results?
**Business understanding**

The project's primary aim is to extract some useful information from the cyber-security dataset so that we may assist in the development of a viable business model for the FutureLearn company's next course.

**Data understanding**

FutureLearn is a British digital education platform that offers a variety of short courses that can be enrolled in and audited for free for a period of five weeks. The company's data file contains over 50 datasets, which were obtained after the course was repeated seven times. Enrollments, types of learners enrolled, learner exit responses, question responses during the course, step activity performed by each student, team members, video statistics of course content, and learners' weekly survey responses are all included in the data file.

The enrollments data set contains the learners' information, including their unique IDs, the course's enrolled and unenrolled dates and times, and additional fields such as gender, nation, age, highest education level, employment location, and current employment status. The vast majority of the students' personal data was not captured. A figure or action that symbolizes universal human nature patterns is referred to as an archetype. The information that categories the students is contained in the archetype data collection.

The specifics of the learners who left the course at what stage and for what reason can be found in the departing survey answer dataset. Each learner's responses to quiz questions conducted at a certain moment in each week are collected in the question response data collection. The results of the quiz may also be seen here. Learners who started and departed the step at particular times are recorded in the step activity data collection. The video statistics data set includes videos of certain steps with titles and information such as time, views, downloads, viewed percentage, and learners' viewed continents.

**Data Preparation**

For this study, I choose to analyse the cyber-security course using enrollment, video statistics, the step-activity dataset, and survey responses from the fourth iteration. The arechtype, question response, and weekly sentiments analysis were all left out because they provided very little information on the assumptions I needed to anticipate.

**Modelling**

I use RStudio, an IDE for creating graphical insights from data sets, in this case.

Installing the Project Template packages to create a project: This part of process was done in Console window.

Loading the Project:
```{r}
load.project
```

#Task which i am doing is that comparing the various variable from the dataset which is given for cybersecurity. So i am comparing the 1st iteration with the last two itertaion to know whther there is a decrease in ppl taking the course.
#Taking the enrolment dataset which was used of the first iteration. 
```{r}
cs=cyber.security.4_enrolments
```
#Loading the dataset into cs1 for data cleaning.
#Different types/techinques of cleaning the data
1. Remove Irrelevant Values
2. Get Rid of Duplicate Values
3. Avoid Typos (and similar errors)
4. Convert Data Types
5. Take Care of Missing Values
#Data Cleaning on the dataset.
1.There are no irrelevant values in the dataset and all data variables are related.
2.Removing the duplicate values.As we can tell from the output that there are no duplicate values in the dataset.
3.There are no similar errors in the dataset.
4.Convert Data Types. Since all the data available in the dataset is of similar data type, Therefore there is no conversion needed.
5.Omitting the missing values.
At-last, cs4 variable contains the cleaned dataset.
```{r}
a=duplicated(cs)#to check whether there is any duplicate data in the data set.
a
b=sapply(a, class)#to check whether the data given is of same data type.
b
cs4=na.omit(cs)
summary(cs4)
```
#Starting the analysing process.
Viewing the number of students enrolled for the course and also checking gender wise for the 1st iteration.
```{r}
s_enrolled=length(unique(cs4$learner_id))
s_enrolled
s_enrolled_gender=table(cs4$gender)
s_enrolled_gender
gender_plot = ggplot(cs1, aes(x = factor(gender))) + 
  geom_bar(stat = "count", width = 0.7, fill = "Red") + theme_minimal() 
gender_plot
pie =gender_plot + coord_polar("y", start=0)+ scale_fill_brewer(palette="Dark2")
pie #should ask.
```



```{r}
employment_plot = ggplot(cyber.security.3_enrolments, aes(x = factor(employment_status))) + 
  geom_bar(stat = "count", width = 0.7, fill = "orange") + theme_minimal() + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
employment_plot
```



```{r}
en_students=as.data.frame(table(cs4$detected_country))
#removing the row without country code.
enrolled_students=en_students[-c(1),]
table(enrolled_students$country)
#selecting the countries with more than 65 enrollments
countries_with_more_than_65_enrollment=enrolled_students[enrolled_students$Freq>65,]
countries_with_more_than_65_enrollment %>%
ggplot(aes(reorder(Var1,-Freq),Freq))+
  geom_col(stat="identity", fill="green",alpha=.8,width = .6)+
  labs(title="No of Students Enrolled vs Countries",x="Countires",
  y="No. of Students Enrolled")+
  theme(plot.title = element_text(hjust = 0.5)) #how to count
```

#We can check how many students are getting unenrolled from leaving survey response dataset and calculate the percentage of students unenrolled from the course.
For 1st iteration.
```{r}
students_unenrolled1=length(cyber.security.1_leaving.survey.responses$left_at)
students_unenrolled1 #Number of students unenrolled at 1st iteration
s_enrolled1=length(unique(cyber.security.1_enrolments$learner_id))#Number of students enrolled
s_enrolled1
Percentage_unenrolled1=(students_unenrolled1/s_enrolled1)*100
Percentage_unenrolled1
```
For 2nd iteration
```{r}
students_unenrolled2=length(cyber.security.2_leaving.survey.responses$left_at)
students_unenrolled2 #Number of students unenrolled at 1st iteration
s_enrolled2=length(unique(cyber.security.2_enrolments$learner_id))#Number of students enrolled
s_enrolled2
Percentage_unenrolled2=(students_unenrolled2/s_enrolled2)*100
Percentage_unenrolled2
```
For 3rd iteration
```{r}
students_unenrolled3=length(cyber.security.3_leaving.survey.responses$left_at)
students_unenrolled3 #Number of students unenrolled at 1st iteration
s_enrolled3=length(unique(cyber.security.3_enrolments$learner_id))#Number of students enrolled
s_enrolled3
Percentage_unenrolled3=(students_unenrolled3/s_enrolled3)*100
Percentage_unenrolled3
```
For 4th iteration
```{r}
students_unenrolled=length(cyber.security.4_leaving.survey.responses$left_at)
students_unenrolled #Number of students unenrolled
s_enrolled #Number of students enrolled
Percentage_unenrolled=(students_unenrolled/s_enrolled)*100
Percentage_unenrolled
```
For 5th iteration
```{r}
students_unenrolled5=length(cyber.security.5_leaving.survey.responses$left_at)
students_unenrolled5 #Number of students unenrolled at 1st iteration
s_enrolled5=length(unique(cyber.security.5_enrolments$learner_id))#Number of students enrolled
s_enrolled5
Percentage_unenrolled5=(students_unenrolled5/s_enrolled5)*100
Percentage_unenrolled5
```
For 6th iteration
```{r}
students_unenrolled6=length(cyber.security.6_leaving.survey.responses$left_at)
students_unenrolled6 #Number of students unenrolled at 1st iteration
s_enrolled6=length(unique(cyber.security.6_enrolments$learner_id))#Number of students enrolled
s_enrolled6
Percentage_unenrolled6=(students_unenrolled6/s_enrolled6)*100
Percentage_unenrolled6
```
For 7th iteration
```{r}
students_unenrolled7=length(cyber.security.7_leaving.survey.responses$left_at)
students_unenrolled7 #Number of students unenrolled at 1st iteration
s_enrolled7=length(unique(cyber.security.7_enrolments$learner_id))#Number of students enrolled
s_enrolled7
Percentage_unenrolled7=(students_unenrolled7/s_enrolled7)*100
Percentage_unenrolled7
```
From the above calculation we can tell that, for the first 3 iteration, the percentage of unenrolled  is 0.But for the 4th iteration there is an increase from 0 to 2%.Likewise, the percentage for 5th, 6th and 7th is 5%,3%, 3.5% respectively.



#Checking the main reason for leaving the course for 4th iteration.
```{r}
gender_plot = ggplot(cyber.security.4_leaving.survey.responses, aes(y = factor(leaving_reason))) + 
  geom_bar(stat = "count", width = 0.7, fill = "steelblue") + theme_minimal() 
gender_plot
```

```{r}
merge=merge.data.frame(cyber.security.4_leaving.survey.responses,cyber.security.4_enrolments,on="learner_id")
unenrolled_students=as.data.frame(table(merge$detected_country))
countries_with_more_than_3_unenrollment=unenrolled_students[unenrolled_students$Freq>3,]
countries_with_more_than_3_unenrollment %>%
ggplot(aes(reorder(Var1,-Freq),Freq))+
  geom_bar(stat="identity", fill="black",alpha=.8,width = .6)+
    labs(title="No of Students Unenrolled vs Countries",x="Countires",
      y="No. of students unenrolled")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
students_unerolled_plot=as.data.frame(table(cyber.security.4_leaving.survey.responses$leaving_reason))
ggplot(students_unerolled_plot,aes(reorder(Var1,Freq),Freq))+
  geom_bar(stat="identity", fill="#f68060", alpha=.8, width=.5) +
    coord_flip() +
   labs(title="No of students unenrolled vs reasons",x="Reasons",y="No .of students unenrolled")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
ggplot(cyber.security.4_video.stats,aes(y=title,x=total_views,))+
  geom_col(stat = "identity",color="green",position = position_dodge())
```


```{r}
g=ggplot(cyber.security.4_video.stats)
g+geom_path(aes(x=step_position,y=europe_views_percentage,colour='Europe view percentage'))+
geom_path(aes(x=step_position,y=oceania_views_percentage,colour='Oceania view percentage'))+
geom_path(aes(x=step_position,y=asia_views_percentage,colour='Asia view percentage'))+
geom_path(aes(x=step_position,y=north_america_views_percentage,colour='North America view percentage'))+
geom_path(aes(x=step_position,y=south_america_views_percentage,colour='South America view percentage '))+
geom_path(aes(x=step_position,y=africa_views_percentage,colour='Africa view percentage'))+
scale_color_discrete("Pattern")+xlab("step position")+ylab("viewed percentage")
```

```{r}
unenrollment.list=list(cyber.security.1_enrolments,cyber.security.2_enrolments,cyber.security.3_enrolments,cyber.security.4_enrolments,cyber.security.5_enrolments,cyber.security.6_enrolments,cyber.security.7_enrolments)

students_unenrollements_over_7_runs=lapply(unenrollment.list, function(cs4) length(unique(cs4$unenrolled_at)))
students=data.frame(students_enrollements_over_7_runs)
colnames(students)=c("1st time","2nd time ","3rd time","4th time","5th time","6th time","7th time")
students
```

